---
title: "19-03-15"
author: "Anirban Pal"
date: "03/19/2015"
output: html_document
---

**Want or need more hours (Q6) x late payment (Q4a)**

```{r, echo=FALSE}
setwd("/home/anirban/Documents/BoulderHousingPartnersData")
load("all.RData")
library("foreign")
library("ggplot2")
library("pander")
library("manipulate")
library("plyr")
library("R2HTML")
panderOptions('table.split.table', Inf)
panderOptions('table.split.cells', Inf)
panderOptions('table.alignment.rownames', 'left')
panderOptions('table.style', 'multiline')
panderOptions('table.emphasize.rownames', FALSE)
ph <- subset(all, PH_or_S8=="PH")
s8 <- subset(all, PH_or_S8=="S8")
```

```{r}
pander(xtabs(formula = ~ Q6 + Q4a, data=ph))
pander(xtabs(formula = ~ Q6 + Q4a, data=s8))
```

PH households show a trend but for S8 households, the pattern is more mixed.

**Sex x expectation future in BHP (Q2a)**

```{r}
pander(xtabs(formula = ~ Q2a + Member.Sex, data=ph))
pander(xtabs(formula = ~ Q2a + Member.Sex, data=s8))
```
PH residents show a clear trend where women are more likely to say that they expect to live in BHP housing for longer time. For S8 households, there is no clear pattern. 

**Citizenship x expectation future in BHP (Q2a)**
```{r}
pander(xtabs(formula = ~ Q2a + Member.Citizen, data=ph))
pander(xtabs(formula = ~ Q2a + Member.Citizen, data=s8))
```
I don't see any clear difference between eligible citizens and ineligible non-citizens.

**TTP x expectation future in BHP (Q2a)**
```{r, echo=FALSE}
all <- subset(all, !is.na(all$Recd.))
xmed<-ddply(all, .(Q2a, PH_or_S8), summarise, med=median(TTP))

ggplot(all, aes(Q2a, TTP)) + geom_boxplot() + 
  geom_text(data = xmed, aes(x = Q2a, y = med, label = med), size = 5, vjust = -0.6) + 
  facet_wrap(~PH_or_S8) + 
   theme(
    strip.text.x = element_text(size = 20, colour = "brown", angle = 0),
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=12, angle = 60, hjust = 1, color="#000033"), 
    axis.text.y = element_text(size=12), 
    axis.title.x = element_text(color="#000033", size=18), 
    axis.title.y = element_text(color="#000033", size=18, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 18)
    ) 
```

It is interesting that those who did not respond to Q2 (or did not participate in the survey) have a lower median TTP than those who did. The difference is higher in S8 than PH. It is also strange that for S8, all three categories of Q2a have the exact same median TTP value. So lets see the distribution of TTP for both PH and S8.

```{r, echo=FALSE}
ggplot(all, aes(TTP)) + geom_bar(binwidth=35, fill='cadetblue', color="white") + 
  facet_wrap(~PH_or_S8) + 
   theme(
    strip.text.x = element_text(size = 20, colour = "brown", angle = 0),
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=12, angle = 60, hjust = 1, color="#000033"), 
    axis.text.y = element_text(size=12), 
    axis.title.x = element_text(color="#000033", size=18), 
    axis.title.y = element_text(color="#000033", size=18, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 18)
    ) 
```

Not sure why S8 has such a skewed distribution of TTP while PH has a more normal distribution. S8 also has more than 70 residents who have TTP=0. Let's also check the distribution of income for both PH and S8 to see if there is a similar pattern.
```{r, echo=FALSE}
ggplot(all, aes(Total.Annual.Income)) + geom_bar(binwidth=1000, fill='cadetblue', color="white") + 
  facet_wrap(~PH_or_S8) + 
   theme(
    strip.text.x = element_text(size = 20, colour = "brown", angle = 0),
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=12, angle = 60, hjust = 1, color="#000033"), 
    axis.text.y = element_text(size=12), 
    axis.title.x = element_text(color="#000033", size=18), 
    axis.title.y = element_text(color="#000033", size=18, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 18)
    ) 
```

There are 46 S8 residents who have income=0 (and 3 who have income above 0 but less than 1000) versus 13 PH residents who have income=0. But the rest of S8 income distribution looks similar to PH.

If we remove households that report BOTH TTP and income to be zero -

```{r, echo=FALSE}
all <- subset(all, !is.na(all$Recd.))
all1 <- subset(all, TTP!=0 | Total.Annual.Income!=0)
xmed<-ddply(all1, .(Q2a, PH_or_S8), summarise, med=median(TTP))

ggplot(all1, aes(Q2a, TTP)) + geom_boxplot() + 
  geom_text(data = xmed, aes(x = Q2a, y = med, label = med), size = 5, vjust = -0.6) + 
  facet_wrap(~PH_or_S8) + 
   theme(
    strip.text.x = element_text(size = 20, colour = "brown", angle = 0),
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=12, angle = 60, hjust = 1, color="#000033"), 
    axis.text.y = element_text(size=12), 
    axis.title.x = element_text(color="#000033", size=18), 
    axis.title.y = element_text(color="#000033", size=18, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 18)
    ) 

xmed<-ddply(all1, .(Q4a, PH_or_S8), summarise, med=median(TTP))

ggplot(all1, aes(Q4a, TTP)) + geom_boxplot() + 
  geom_text(data = xmed, aes(x = Q4a, y = med, label = med), size = 5, vjust = -0.6) + 
  facet_wrap(~PH_or_S8) + 
   theme(
    strip.text.x = element_text(size = 20, colour = "brown", angle = 0),
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=12, angle = 60, hjust = 1, color="#000033"), 
    axis.text.y = element_text(size=12), 
    axis.title.x = element_text(color="#000033", size=18), 
    axis.title.y = element_text(color="#000033", size=18, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 18)
    ) 

xmed<-ddply(all1, .(Q2a, PH_or_S8), summarise, med=median(Total.Annual.Income))

ggplot(all1, aes(Q2a, Total.Annual.Income)) + geom_boxplot() + 
  geom_text(data = xmed, aes(x = Q2a, y = med, label = med), size = 5, vjust = -0.6) + 
  facet_wrap(~PH_or_S8) + 
   theme(
    strip.text.x = element_text(size = 20, colour = "brown", angle = 0),
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=12, angle = 60, hjust = 1, color="#000033"), 
    axis.text.y = element_text(size=12), 
    axis.title.x = element_text(color="#000033", size=18), 
    axis.title.y = element_text(color="#000033", size=18, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 18)
    ) 

xmed<-ddply(all1, .(Q4a, PH_or_S8), summarise, med=median(Total.Annual.Income))

ggplot(all1, aes(Q4a, Total.Annual.Income)) + geom_boxplot() + 
  geom_text(data = xmed, aes(x = Q4a, y = med, label = med), size = 5, vjust = -0.6) + 
  facet_wrap(~PH_or_S8) + 
   theme(
    strip.text.x = element_text(size = 20, colour = "brown", angle = 0),
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=12, angle = 60, hjust = 1, color="#000033"), 
    axis.text.y = element_text(size=12), 
    axis.title.x = element_text(color="#000033", size=18), 
    axis.title.y = element_text(color="#000033", size=18, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 18)
    ) 
```

**Crowding (Number of family members / Bedrooms) x expectation future in BHP (Q2a)**
```{r, echo=FALSE}
all <- subset(all, !is.na(all$Recd.))
all$Crowding<-round(all$Family.Members/all$Bedrooms, 2)
xmed<-ddply(all, .(Q2a, PH_or_S8), summarise, med=median(Crowding))

ggplot(all, aes(Q2a, Crowding)) + geom_boxplot() + 
  geom_text(data = xmed, aes(x = Q2a, y = med, label = med), size = 5, vjust = -0.6) + 
  facet_wrap(~PH_or_S8) + 
   theme(
    strip.text.x = element_text(size = 20, colour = "brown", angle = 0),
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=12, angle = 60, hjust = 1, color="#000033"), 
    axis.text.y = element_text(size=12), 
    axis.title.x = element_text(color="#000033", size=18), 
    axis.title.y = element_text(color="#000033", size=18, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 18)
    ) 
```


**Children under 13 (HH.Members.under.age.13) X expectation future in BHP (Q2a)**
```{r, echo=FALSE}
all <- subset(all, !is.na(all$Recd.))
xmed<-ddply(all, .(Q2a, PH_or_S8), summarise, med=median(HH.Members.under.age.13))

ggplot(all, aes(Q2a, HH.Members.under.age.13)) + geom_boxplot() + 
  geom_text(data = xmed, aes(x = Q2a, y = med, label = med), size = 5, vjust = -0.6) + 
  facet_wrap(~PH_or_S8) + 
   theme(
    strip.text.x = element_text(size = 20, colour = "brown", angle = 0),
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=12, angle = 60, hjust = 1, color="#000033"), 
    axis.text.y = element_text(size=12), 
    axis.title.x = element_text(color="#000033", size=18), 
    axis.title.y = element_text(color="#000033", size=18, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 18)
    ) 
```
```{r}
# Q19 (Children <13?) vs. Q2a (expectation future in BHP)
pander(xtabs(formula = ~ Q2a + Q19, data=ph))
pander(xtabs(formula = ~ Q2a + Q19, data=s8))
```
There is no clear pattern of difference between those who have children and those who don't.

**Single parent fam x expectation future in BHP (Q2a)**
```{r}
# Q19 (Children <13?) vs. Q2a (expectation future in BHP)
pander(xtabs(formula = ~ Q2a + Single.Parent.HH, data=ph))
pander(xtabs(formula = ~ Q2a + Single.Parent.HH, data=s8))

pander(xtabs(formula = ~ Q36_1 + Single.Parent.HH, data=ph))
pander(xtabs(formula = ~ Q36_1 + Single.Parent.HH, data=s8))

pander(round(prop.table(xtabs(formula = ~ Q36_1 + Single.Parent.HH, data=ph), 2)*100, 0))
pander(round(prop.table(xtabs(formula = ~ Q36_1 + Single.Parent.HH, data=s8), 2)*100, 0))

pander(round(prop.table(xtabs(formula = ~ Q4a + Single.Parent.HH, data=ph), 2)*100, 0))
pander(round(prop.table(xtabs(formula = ~ Q4a + Single.Parent.HH, data=s8), 2)*100, 0))
```

This is interesting. Among single parent households in S8, we see the share of those who say they will be living in BHP housing for upto 2 years is higher than those who say they will be there for 5 or more years. 

**Children under 13 x late payment (Q4a)**
```{r, echo=FALSE}
all <- subset(all, !is.na(all$Recd.))
xmed<-ddply(all, .(Q4a, PH_or_S8), summarise, med=median(HH.Members.under.age.13))

ggplot(all, aes(Q4a, HH.Members.under.age.13)) + geom_boxplot() + 
  geom_text(data = xmed, aes(x = Q4a, y = med, label = med), size = 5, vjust = -0.6) + 
  facet_wrap(~PH_or_S8) + 
   theme(
    strip.text.x = element_text(size = 20, colour = "brown", angle = 0),
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=12, angle = 60, hjust = 1, color="#000033"), 
    axis.text.y = element_text(size=12), 
    axis.title.x = element_text(color="#000033", size=18), 
    axis.title.y = element_text(color="#000033", size=18, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 18)
    ) 
```
```{r}
# Q19 (Children <13?) vs. Q4a (late payment)
pander(xtabs(formula = ~ Q4a + Q19, data=ph))
pander(xtabs(formula = ~ Q4a + Q19, data=s8))
```

Those who have children are more likely to pay rent late.

**Single parent fam x late payment (Q4a)**

```{r}
pander(xtabs(formula = ~ Q4a + Single.Parent.HH, data=ph))
pander(xtabs(formula = ~ Q4a + Single.Parent.HH, data=s8))
```
Single parent households are more likely to pay rent late.

**Employment status**
```{r}
pander(prop.table(xtabs(formula = ~ Q5 + Q4a, data=ph), 1))
pander(prop.table(xtabs(formula = ~ Q5 + Q4a, data=s8), 1))

pander(xtabs(formula = ~ Q5 + Q4a, data=ph))
pander(xtabs(formula = ~ Q5 + Q4a, data=s8))

pander(round(prop.table(xtabs(formula = ~ Q5 + Q2a, data=ph), 1)*100, 1))
pander(round(prop.table(xtabs(formula = ~ Q5 + Q2a, data=s8), 1)*100, 1))

pander(xtabs(formula = ~ Q5 + Q2a, data=ph))
pander(xtabs(formula = ~ Q5 + Q2a, data=s8))

pander(round(prop.table(xtabs(formula = ~ Q5 + Q36_1, data=ph), 1)*100, 1))
pander(round(prop.table(xtabs(formula = ~ Q5 + Q36_1, data=s8), 1)*100, 1))

pander(xtabs(formula = ~ Q5 + Q36_1, data=ph))
pander(xtabs(formula = ~ Q5 + Q36_1, data=s8))
```


**Need or want more hours**
```{r}
pander(prop.table(xtabs(formula = ~ Q6 + Q4a, data=ph), 1))
pander(prop.table(xtabs(formula = ~ Q6 + Q4a, data=s8), 1))

pander(xtabs(formula = ~ Q6 + Q4a, data=ph))
pander(xtabs(formula = ~ Q6 + Q4a, data=s8))

pander(round(prop.table(xtabs(formula = ~ Q6 + Q2a, data=ph), 1)*100, 0))
pander(round(prop.table(xtabs(formula = ~ Q6 + Q2a, data=s8), 1)*100, 0))

pander(xtabs(formula = ~ Q6 + Q2a, data=ph))
pander(xtabs(formula = ~ Q6 + Q2a, data=s8))

pander(round(prop.table(xtabs(formula = ~ Q6 + Q36_1, data=ph), 2)*100, 0))
pander(round(prop.table(xtabs(formula = ~ Q6 + Q36_1, data=s8), 2)*100, 0))

pander(xtabs(formula = ~ Q6 + Q36_1, data=ph))
pander(xtabs(formula = ~ Q6 + Q36_1, data=s8))
```


**Cost of housing relative to income**

We construct a new variable, housingcost = TTP*12/Income. The Maximum value of this variable is is 7.35, median is 0.32 and mean is 0.38. There are 4 respondents in S8 and one respondent in PH who have housingcost more than 1. Let us exclude 3 PH and 5 S8 HHs who have housingcost > 0.75; They are clearly outliers. Summary statistics and distribution of housingcost after removing the outliers is shown below.

```{r, echo=FALSE}
all <- subset(all, !is.na(all$Recd.))
all1 <- subset(all, TTP!=0 & Total.Annual.Income!=0)


all1$housingcost<-all1$TTP*12/all1$Total.Annual.Income

x <- subset(all1, housingcost>0.75)
all1 <- subset(all1, housingcost<=0.75)
summary(all1$housingcost)
ggplot(all1, aes(housingcost)) + geom_bar(binwidth=0.05, fill="cadetblue", color="white") +facet_wrap(~PH_or_S8)

xmed<-ddply(all1, .(Q2a, PH_or_S8), summarise, med=round(median(housingcost), 3))

ggplot(all1, aes(Q2a, housingcost)) + geom_boxplot() + 
  geom_text(data = xmed, aes(x = Q2a, y = med, label = med), size = 5, vjust = -0.6) + 
  facet_wrap(~PH_or_S8) + 
   theme(
    strip.text.x = element_text(size = 20, colour = "brown", angle = 0),
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=12, angle = 60, hjust = 1, color="#000033"), 
    axis.text.y = element_text(size=12), 
    axis.title.x = element_text(color="#000033", size=18), 
    axis.title.y = element_text(color="#000033", size=18, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 18)
    ) 

xmed<-ddply(all1, .(Q4a, PH_or_S8), summarise, med=round(median(housingcost), 3))

ggplot(all1, aes(Q4a, housingcost)) + geom_boxplot() + 
  geom_text(data = xmed, aes(x = Q4a, y = med, label = med), size = 5, vjust = -0.6) + 
  facet_wrap(~PH_or_S8) + 
   theme(
    strip.text.x = element_text(size = 20, colour = "brown", angle = 0),
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=12, angle = 60, hjust = 1, color="#000033"), 
    axis.text.y = element_text(size=12), 
    axis.title.x = element_text(color="#000033", size=18), 
    axis.title.y = element_text(color="#000033", size=18, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 18)
    ) 

xmed<-ddply(all1, .(Q36_1, PH_or_S8), summarise, med=round(median(housingcost), 3))

ggplot(all1, aes(Q36_1, housingcost)) + geom_boxplot() + 
  geom_text(data = xmed, aes(x = Q36_1, y = med, label = med), size = 5, vjust = -0.6) + 
  facet_wrap(~PH_or_S8) + 
   theme(
    strip.text.x = element_text(size = 20, colour = "brown", angle = 0),
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=12, angle = 60, hjust = 1, color="#000033"), 
    axis.text.y = element_text(size=12), 
    axis.title.x = element_text(color="#000033", size=18), 
    axis.title.y = element_text(color="#000033", size=18, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 18)
    ) 
```

**Income per family member after paying for housing**

We construct a new variable, per.person.income = Income - TTP*12/number of family members. 

```{r, echo=FALSE}
all <- subset(all, !is.na(all$Recd.))
all1 <- subset(all, TTP!=0 & Total.Annual.Income!=0)

all1$per.person.income<-(all1$Total.Annual.Income-(all1$TTP*12))/all1$Family.Members

ggplot(all1, aes(per.person.income)) + geom_bar(fill="cadetblue", color="white") +facet_wrap(~PH_or_S8)

xmed<-ddply(all1, .(Q2a, PH_or_S8), summarise, med=round(median(per.person.income), 3))

ggplot(all1, aes(Q2a, per.person.income)) + geom_boxplot() + 
  geom_text(data = xmed, aes(x = Q2a, y = med, label = med), size = 5, vjust = -0.6) + 
  facet_wrap(~PH_or_S8) + 
   theme(
    strip.text.x = element_text(size = 20, colour = "brown", angle = 0),
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=12, angle = 60, hjust = 1, color="#000033"), 
    axis.text.y = element_text(size=12), 
    axis.title.x = element_text(color="#000033", size=18), 
    axis.title.y = element_text(color="#000033", size=18, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 18)
    ) 

xmed<-ddply(all1, .(Q4a, PH_or_S8), summarise, med=round(median(per.person.income), 3))

ggplot(all1, aes(Q4a, per.person.income)) + geom_boxplot() + 
  geom_text(data = xmed, aes(x = Q4a, y = med, label = med), size = 5, vjust = -0.6) + 
  facet_wrap(~PH_or_S8) + 
   theme(
    strip.text.x = element_text(size = 20, colour = "brown", angle = 0),
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=12, angle = 60, hjust = 1, color="#000033"), 
    axis.text.y = element_text(size=12), 
    axis.title.x = element_text(color="#000033", size=18), 
    axis.title.y = element_text(color="#000033", size=18, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 18)
    ) 

xmed<-ddply(all1, .(Q36_1, PH_or_S8), summarise, med=round(median(per.person.income), 3))

ggplot(all1, aes(Q36_1, per.person.income)) + geom_boxplot() + 
  geom_text(data = xmed, aes(x = Q36_1, y = med, label = med), size = 5, vjust = -0.6) + 
  facet_wrap(~PH_or_S8) + 
   theme(
    strip.text.x = element_text(size = 20, colour = "brown", angle = 0),
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=12, angle = 60, hjust = 1, color="#000033"), 
    axis.text.y = element_text(size=12), 
    axis.title.x = element_text(color="#000033", size=18), 
    axis.title.y = element_text(color="#000033", size=18, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 18)
    ) 
```

```{r}
pander(round(prop.table(xtabs(formula = ~ Q4a + Q5, data=ph), 2)*100, 0))
pander(round(prop.table(xtabs(formula = ~ Q4a + Q5, data=s8), 2)*100, 0))

pander(round(prop.table(xtabs(formula = ~ Q2a + Q5, data=ph), 2)*100, 0))
pander(round(prop.table(xtabs(formula = ~ Q2a + Q5, data=s8), 2)*100, 0))
```

**Employment Status**


```{r, echo=FALSE}
rm(x, y, xy)
x <- as.data.frame(prop.table(xtabs(formula = ~ Q4a + Q5, data=s8), 2))
x$phs8 <- "S8"
y <- as.data.frame(prop.table(xtabs(formula = ~ Q4a + Q5, data=ph), 2))
y$phs8 <- "PH"
xy <- rbind(x, y)
xy$phs8 <- as.factor(xy$phs8)
ggplot(xy, aes(Q5, Freq)) + geom_bar(aes(fill=Q4a), stat="identity", position="stack") + facet_wrap(~phs8) +
   theme(
    strip.text.x = element_text(size = 20, colour = "brown", angle = 0),
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=12, angle = 75, hjust = 1, color="#000033"), 
    axis.text.y = element_text(size=12), 
    axis.title.x = element_text(color="#000033", size=18), 
    axis.title.y = element_text(color="#000033", size=18, vjust=2),
    legend.text = element_text(colour="#000033", size = 10)
    ) 

rm(x, y, xy)
x <- as.data.frame(prop.table(xtabs(formula = ~ Q2a + Q5, data=s8), 2))
x$phs8 <- "S8"
y <- as.data.frame(prop.table(xtabs(formula = ~ Q2a + Q5, data=ph), 2))
y$phs8 <- "PH"
xy <- rbind(x, y)
xy$phs8 <- as.factor(xy$phs8)
ggplot(xy, aes(Q5, Freq)) + geom_bar(aes(fill=Q2a), stat="identity", position="stack") + facet_wrap(~phs8) +
   theme(
    strip.text.x = element_text(size = 20, colour = "brown", angle = 0),
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=12, angle = 75, hjust = 1, color="#000033"), 
    axis.text.y = element_text(size=12), 
    axis.title.x = element_text(color="#000033", size=18), 
    axis.title.y = element_text(color="#000033", size=18, vjust=2),
    legend.text = element_text(colour="#000033", size = 10)
    ) 

rm(x, y, xy)
x <- as.data.frame(prop.table(xtabs(formula = ~ Q36_1 + Q5, data=s8), 2))
x$phs8 <- "S8"
y <- as.data.frame(prop.table(xtabs(formula = ~ Q36_1 + Q5, data=ph), 2))
y$phs8 <- "PH"
xy <- rbind(x, y)
xy$phs8 <- as.factor(xy$phs8)
ggplot(xy, aes(Q5, Freq)) + geom_bar(aes(fill=Q36_1), stat="identity", position="stack") + facet_wrap(~phs8) +
   theme(
    strip.text.x = element_text(size = 20, colour = "brown", angle = 0),
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=12, angle = 75, hjust = 1, color="#000033"), 
    axis.text.y = element_text(size=12), 
    axis.title.x = element_text(color="#000033", size=18), 
    axis.title.y = element_text(color="#000033", size=18, vjust=2),
    legend.text = element_text(colour="#000033", size = 10)
    ) 
```


**Need/Want more hours**


```{r, echo=FALSE}
rm(x, y, xy)
x <- as.data.frame(prop.table(xtabs(formula = ~ Q4a + Q6, data=s8), 2))
x$phs8 <- "S8"
y <- as.data.frame(prop.table(xtabs(formula = ~ Q4a + Q6, data=ph), 2))
y$phs8 <- "PH"
xy <- rbind(x, y)
xy$phs8 <- as.factor(xy$phs8)
ggplot(xy, aes(Q6, Freq)) + geom_bar(aes(fill=Q4a), stat="identity", position="stack") + facet_wrap(~phs8) +
   theme(
    strip.text.x = element_text(size = 20, colour = "brown", angle = 0),
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=12, angle = 45, hjust = 1, color="#000033"), 
    axis.text.y = element_text(size=12), 
    axis.title.x = element_text(color="#000033", size=18), 
    axis.title.y = element_text(color="#000033", size=18, vjust=2),
    legend.text = element_text(colour="#000033", size = 10)
    ) 

rm(x, y, xy)
x <- as.data.frame(prop.table(xtabs(formula = ~ Q2a + Q6, data=s8), 2))
x$phs8 <- "S8"
y <- as.data.frame(prop.table(xtabs(formula = ~ Q2a + Q6, data=ph), 2))
y$phs8 <- "PH"
xy <- rbind(x, y)
xy$phs8 <- as.factor(xy$phs8)
ggplot(xy, aes(Q6, Freq)) + geom_bar(aes(fill=Q2a), stat="identity", position="stack") + facet_wrap(~phs8) +
   theme(
    strip.text.x = element_text(size = 20, colour = "brown", angle = 0),
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=12, angle = 45, hjust = 1, color="#000033"), 
    axis.text.y = element_text(size=12), 
    axis.title.x = element_text(color="#000033", size=18), 
    axis.title.y = element_text(color="#000033", size=18, vjust=2),
    legend.text = element_text(colour="#000033", size = 10)
    ) 

rm(x, y, xy)
x <- as.data.frame(prop.table(xtabs(formula = ~ Q36_1 + Q6, data=s8), 2))
x$phs8 <- "S8"
y <- as.data.frame(prop.table(xtabs(formula = ~ Q36_1 + Q6, data=ph), 2))
y$phs8 <- "PH"
xy <- rbind(x, y)
xy$phs8 <- as.factor(xy$phs8)
ggplot(xy, aes(Q6, Freq)) + geom_bar(aes(fill=Q36_1), stat="identity", position="stack") + facet_wrap(~phs8) +
   theme(
    strip.text.x = element_text(size = 20, colour = "brown", angle = 0),
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=12, angle = 45, hjust = 1, color="#000033"), 
    axis.text.y = element_text(size=12), 
    axis.title.x = element_text(color="#000033", size=18), 
    axis.title.y = element_text(color="#000033", size=18, vjust=2),
    legend.text = element_text(colour="#000033", size = 10)
    ) 
```


**Single parent**


```{r, echo=FALSE}
rm(x, y, xy)
x <- as.data.frame(prop.table(xtabs(formula = ~ Q4a + Single.Parent.HH, data=s8), 2))
x$phs8 <- "S8"
y <- as.data.frame(prop.table(xtabs(formula = ~ Q4a + Single.Parent.HH, data=ph), 2))
y$phs8 <- "PH"
xy <- rbind(x, y)
xy <- subset(xy, Single.Parent.HH!="Unknown")
xy$phs8 <- as.factor(xy$phs8)
ggplot(xy, aes(Single.Parent.HH, Freq)) + geom_bar(aes(fill=Q4a), stat="identity", position="stack") + facet_wrap(~phs8) +
   theme(
    strip.text.x = element_text(size = 20, colour = "brown", angle = 0),
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=12, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(size=12), 
    axis.title.x = element_text(color="#000033", size=18), 
    axis.title.y = element_text(color="#000033", size=18, vjust=2),
    legend.text = element_text(colour="#000033", size = 10)
    ) 

rm(x, y, xy)
x <- as.data.frame(prop.table(xtabs(formula = ~ Q2a + Single.Parent.HH, data=s8), 2))
x$phs8 <- "S8"
y <- as.data.frame(prop.table(xtabs(formula = ~ Q2a + Single.Parent.HH, data=ph), 2))
y$phs8 <- "PH"
xy <- rbind(x, y)
xy <- subset(xy, Single.Parent.HH!="Unknown")
xy$phs8 <- as.factor(xy$phs8)
ggplot(xy, aes(Single.Parent.HH, Freq)) + geom_bar(aes(fill=Q2a), stat="identity", position="stack") + facet_wrap(~phs8) +
   theme(
    strip.text.x = element_text(size = 20, colour = "brown", angle = 0),
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=12, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(size=12), 
    axis.title.x = element_text(color="#000033", size=18), 
    axis.title.y = element_text(color="#000033", size=18, vjust=2),
    legend.text = element_text(colour="#000033", size = 10)
    ) 

rm(x, y, xy)
x <- as.data.frame(prop.table(xtabs(formula = ~ Q36_1 + Single.Parent.HH, data=s8), 2))
x$phs8 <- "S8"
y <- as.data.frame(prop.table(xtabs(formula = ~ Q36_1 + Single.Parent.HH, data=ph), 2))
y$phs8 <- "PH"
xy <- rbind(x, y)
xy <- subset(xy, Single.Parent.HH!="Unknown")
xy$phs8 <- as.factor(xy$phs8)
xy$Q36_1<-as.ordered(xy$Q36_1)
ggplot(xy, aes(Single.Parent.HH, Freq)) + geom_bar(aes(fill=Q36_1), stat="identity", position="stack") + facet_wrap(~phs8) +
   theme(
    strip.text.x = element_text(size = 20, colour = "brown", angle = 0),
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=12, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(size=12), 
    axis.title.x = element_text(color="#000033", size=18), 
    axis.title.y = element_text(color="#000033", size=18, vjust=2),
    legend.text = element_text(colour="#000033", size = 10)
    ) 

```


**Gender of household head**


```{r, echo=FALSE}
rm(x, y, xy)
x <- as.data.frame(prop.table(xtabs(formula = ~ Q4a + Member.Sex, data=s8), 2))
x$phs8 <- "S8"
y <- as.data.frame(prop.table(xtabs(formula = ~ Q4a + Member.Sex, data=ph), 2))
y$phs8 <- "PH"
xy <- rbind(x, y)
xy$phs8 <- as.factor(xy$phs8)
ggplot(xy, aes(Member.Sex, Freq)) + geom_bar(aes(fill=Q4a), stat="identity", position="stack") + facet_wrap(~phs8) +
   theme(
    strip.text.x = element_text(size = 20, colour = "brown", angle = 0),
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=12, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(size=12), 
    axis.title.x = element_text(color="#000033", size=18), 
    axis.title.y = element_text(color="#000033", size=18, vjust=2),
    legend.text = element_text(colour="#000033", size = 10)
    ) 

rm(x, y, xy)
x <- as.data.frame(prop.table(xtabs(formula = ~ Q2a + Member.Sex, data=s8), 2))
x$phs8 <- "S8"
y <- as.data.frame(prop.table(xtabs(formula = ~ Q2a + Member.Sex, data=ph), 2))
y$phs8 <- "PH"
xy <- rbind(x, y)
xy$phs8 <- as.factor(xy$phs8)
ggplot(xy, aes(Member.Sex, Freq)) + geom_bar(aes(fill=Q2a), stat="identity", position="stack") + facet_wrap(~phs8) +
   theme(
    strip.text.x = element_text(size = 20, colour = "brown", angle = 0),
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=12, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(size=12), 
    axis.title.x = element_text(color="#000033", size=18), 
    axis.title.y = element_text(color="#000033", size=18, vjust=2),
    legend.text = element_text(colour="#000033", size = 10)
    ) 

rm(x, y, xy)
x <- as.data.frame(prop.table(xtabs(formula = ~ Q36_1 + Member.Sex, data=s8), 2))
x$phs8 <- "S8"
y <- as.data.frame(prop.table(xtabs(formula = ~ Q36_1 + Member.Sex, data=ph), 2))
y$phs8 <- "PH"
xy <- rbind(x, y)
xy$phs8 <- as.factor(xy$phs8)
ggplot(xy, aes(Member.Sex, Freq)) + geom_bar(aes(fill=Q36_1), stat="identity", position="stack") + facet_wrap(~phs8) +
   theme(
    strip.text.x = element_text(size = 20, colour = "brown", angle = 0),
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=12, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(size=12), 
    axis.title.x = element_text(color="#000033", size=18), 
    axis.title.y = element_text(color="#000033", size=18, vjust=2),
    legend.text = element_text(colour="#000033", size = 10)
    ) 
```


**Medical problem and not go to see a doctor**


```{r, echo=FALSE}
rm(x, y, xy)
x <- as.data.frame(prop.table(xtabs(formula = ~ Q4a + Q31, data=s8), 2))
x$phs8 <- "S8"
y <- as.data.frame(prop.table(xtabs(formula = ~ Q4a + Q31, data=ph), 2))
y$phs8 <- "PH"
xy <- rbind(x, y)
xy$phs8 <- as.factor(xy$phs8)
ggplot(xy, aes(Q31, Freq)) + geom_bar(aes(fill=Q4a), stat="identity", position="stack") + facet_wrap(~phs8) +
   theme(
    strip.text.x = element_text(size = 20, colour = "brown", angle = 0),
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=12, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(size=12), 
    axis.title.x = element_text(color="#000033", size=18), 
    axis.title.y = element_text(color="#000033", size=18, vjust=2),
    legend.text = element_text(colour="#000033", size = 10)
    ) 

rm(x, y, xy)
x <- as.data.frame(prop.table(xtabs(formula = ~ Q2a + Q31, data=s8), 2))
x$phs8 <- "S8"
y <- as.data.frame(prop.table(xtabs(formula = ~ Q2a + Q31, data=ph), 2))
y$phs8 <- "PH"
xy <- rbind(x, y)
xy$phs8 <- as.factor(xy$phs8)
ggplot(xy, aes(Q31, Freq)) + geom_bar(aes(fill=Q2a), stat="identity", position="stack") + facet_wrap(~phs8) +
   theme(
    strip.text.x = element_text(size = 20, colour = "brown", angle = 0),
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=12, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(size=12), 
    axis.title.x = element_text(color="#000033", size=18), 
    axis.title.y = element_text(color="#000033", size=18, vjust=2),
    legend.text = element_text(colour="#000033", size = 10)
    ) 

rm(x, y, xy)
x <- as.data.frame(prop.table(xtabs(formula = ~ Q36_1 + Q31, data=s8), 2))
x$phs8 <- "S8"
y <- as.data.frame(prop.table(xtabs(formula = ~ Q36_1 + Q31, data=ph), 2))
y$phs8 <- "PH"
xy <- rbind(x, y)
xy$phs8 <- as.factor(xy$phs8)
ggplot(xy, aes(Q31, Freq)) + geom_bar(aes(fill=Q36_1), stat="identity", position="stack") + facet_wrap(~phs8) +
   theme(
    strip.text.x = element_text(size = 20, colour = "brown", angle = 0),
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=12, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(size=12), 
    axis.title.x = element_text(color="#000033", size=18), 
    axis.title.y = element_text(color="#000033", size=18, vjust=2),
    legend.text = element_text(colour="#000033", size = 10)
    ) 
```

**Free or reduced lunch**


```{r, echo=FALSE}
rm(x, y, xy)
x <- as.data.frame(prop.table(xtabs(formula = ~ Q4a + Q25_5, data=s8), 2))
x$phs8 <- "S8"
y <- as.data.frame(prop.table(xtabs(formula = ~ Q4a + Q25_5, data=ph), 2))
y$phs8 <- "PH"
xy <- rbind(x, y)
xy$phs8 <- as.factor(xy$phs8)
ggplot(xy, aes(Q25_5, Freq)) + geom_bar(aes(fill=Q4a), stat="identity", position="stack") + facet_wrap(~phs8) +
   theme(
    strip.text.x = element_text(size = 20, colour = "brown", angle = 0),
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=12, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(size=12), 
    axis.title.x = element_text(color="#000033", size=18), 
    axis.title.y = element_text(color="#000033", size=18, vjust=2),
    legend.text = element_text(colour="#000033", size = 10)
    ) 

rm(x, y, xy)
x <- as.data.frame(prop.table(xtabs(formula = ~ Q2a + Q25_5, data=s8), 2))
x$phs8 <- "S8"
y <- as.data.frame(prop.table(xtabs(formula = ~ Q2a + Q25_5, data=ph), 2))
y$phs8 <- "PH"
xy <- rbind(x, y)
xy$phs8 <- as.factor(xy$phs8)
ggplot(xy, aes(Q25_5, Freq)) + geom_bar(aes(fill=Q2a), stat="identity", position="stack") + facet_wrap(~phs8) +
   theme(
    strip.text.x = element_text(size = 20, colour = "brown", angle = 0),
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=12, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(size=12), 
    axis.title.x = element_text(color="#000033", size=18), 
    axis.title.y = element_text(color="#000033", size=18, vjust=2),
    legend.text = element_text(colour="#000033", size = 10)
    ) 

rm(x, y, xy)
x <- as.data.frame(prop.table(xtabs(formula = ~ Q36_1 + Q25_5, data=s8), 2))
x$phs8 <- "S8"
y <- as.data.frame(prop.table(xtabs(formula = ~ Q36_1 + Q25_5, data=ph), 2))
y$phs8 <- "PH"
xy <- rbind(x, y)
xy$phs8 <- as.factor(xy$phs8)
ggplot(xy, aes(Q25_5, Freq)) + geom_bar(aes(fill=Q36_1), stat="identity", position="stack") + facet_wrap(~phs8) +
   theme(
    strip.text.x = element_text(size = 20, colour = "brown", angle = 0),
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=12, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(size=12), 
    axis.title.x = element_text(color="#000033", size=18), 
    axis.title.y = element_text(color="#000033", size=18, vjust=2),
    legend.text = element_text(colour="#000033", size = 10)
    ) 
```


**Medicaid**


```{r, echo=FALSE}
rm(x, y, xy)
x <- as.data.frame(prop.table(xtabs(formula = ~ Q4a + Q25_2, data=s8), 2))
x$phs8 <- "S8"
y <- as.data.frame(prop.table(xtabs(formula = ~ Q4a + Q25_2, data=ph), 2))
y$phs8 <- "PH"
xy <- rbind(x, y)
xy$phs8 <- as.factor(xy$phs8)
ggplot(xy, aes(Q25_2, Freq)) + geom_bar(aes(fill=Q4a), stat="identity", position="stack") + facet_wrap(~phs8) +
   theme(
    strip.text.x = element_text(size = 20, colour = "brown", angle = 0),
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=12, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(size=12), 
    axis.title.x = element_text(color="#000033", size=18), 
    axis.title.y = element_text(color="#000033", size=18, vjust=2),
    legend.text = element_text(colour="#000033", size = 10)
    ) 

rm(x, y, xy)
x <- as.data.frame(prop.table(xtabs(formula = ~ Q2a + Q25_2, data=s8), 2))
x$phs8 <- "S8"
y <- as.data.frame(prop.table(xtabs(formula = ~ Q2a + Q25_2, data=ph), 2))
y$phs8 <- "PH"
xy <- rbind(x, y)
xy$phs8 <- as.factor(xy$phs8)
ggplot(xy, aes(Q25_2, Freq)) + geom_bar(aes(fill=Q2a), stat="identity", position="stack") + facet_wrap(~phs8) +
   theme(
    strip.text.x = element_text(size = 20, colour = "brown", angle = 0),
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=12, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(size=12), 
    axis.title.x = element_text(color="#000033", size=18), 
    axis.title.y = element_text(color="#000033", size=18, vjust=2),
    legend.text = element_text(colour="#000033", size = 10)
    ) 

rm(x, y, xy)
x <- as.data.frame(prop.table(xtabs(formula = ~ Q36_1 + Q25_2, data=s8), 2))
x$phs8 <- "S8"
y <- as.data.frame(prop.table(xtabs(formula = ~ Q36_1 + Q25_2, data=ph), 2))
y$phs8 <- "PH"
xy <- rbind(x, y)
xy$phs8 <- as.factor(xy$phs8)
ggplot(xy, aes(Q25_2, Freq)) + geom_bar(aes(fill=Q36_1), stat="identity", position="stack") + facet_wrap(~phs8) +
   theme(
    strip.text.x = element_text(size = 20, colour = "brown", angle = 0),
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=12, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(size=12), 
    axis.title.x = element_text(color="#000033", size=18), 
    axis.title.y = element_text(color="#000033", size=18, vjust=2),
    legend.text = element_text(colour="#000033", size = 10)
    ) 
```