---
title: "Additional Data Exploration"
author: "Anirban Pal"
date: "02/21/2015"
output: html_document
---

```{r, echo=FALSE}
setwd("/home/anirban/Documents/BoulderHousingPartnersData")
library("foreign")
library("ggplot2")
library("pander")
library("manipulate")
panderOptions('table.split.table', Inf)
panderOptions('table.split.cells', Inf)
panderOptions('table.alignment.rownames', 'left')
panderOptions('table.style', 'multiline')
panderOptions('table.emphasize.rownames', FALSE)
ph <- read.spss('PH.sav', to.data.frame=TRUE) ## Import PH data from SPSS files.
s8 <- read.spss('S8_NA_999.sav', to.data.frame=TRUE) ## Import S8 data from SPSS files.
s8$Surveyed <- "Yes"
ph$Surveyed <- "Yes"

# ph_loc <- read.csv("PH_Loc.csv") ## This is not needed any more. PH location site codes are already in phadditional file.
phadditional <- read.csv("ph.csv")
s8additional <- read.csv("s8.csv")
# ph_loc <- ph_loc[1:67, 6:7]
# names(ph_loc)[2] <- "location"
names(phadditional)[1] <- "location"
names(s8additional)[1] <- "location"
names(phadditional)[2] <- "TCode"
names(s8additional)[2] <- "TCode"
s8$TCode<-tolower(s8$TCode)
ph$TCode<-tolower(ph$TCode)


### Some of the trouble TCodes are as follows: 
# t0000151
# a0000696
# a0001948
# t0001972

#subset(s8, TCode=="a0000696")
s8[243, 1] <- "t0000696"

#subset(ph, TCode=="t0000151")
#subset(phadditional, TCode=="a0000151")
ph[38, 1] <- "a0000151"

#subset(s8, TCode=="a0001948")
#subset(s8additional, TCode=="t0001948")
s8[144, 1]<-"t0001948"

#subset(s8, TCode=="t0001972")
#subset(s8additional, TCode=="a0001972")
s8[145, 1]

# ph_loc$location <- as.factor(as.integer(ph_loc$location)) # Make "location" a categorical variable.


ph$Q1 <- factor(ph$Q1,
                levels = c("I owned my home", "I lived in private market rental housing (including student housing)", "I lived in subsidized housing (for example, Section 8, Public Housing)", "I lived with family and friends", "I was homeless"),
                labels = c("Owned my home", "Market rental", "Subsidized housing", "With family/friends", "Was homeless"))

s8$Q1 <- factor(s8$Q1,
                levels = c("I owned my home", "I lived in private market rental housing (including student housing)", "I lived in subsidized housing (for example, Section 8, Public Housing)", "I lived with family and friends", "I was homeless"),
                labels = c("Owned my home", "Market rental", "Subsidized housing", "With family/friends", "Was homeless"))

ph <- ph[1:85, ]      ## Rows beyond row 85 do not have any data. So we remove those rows.
s8 <- s8[-35, ]       ## Row 35 does not have any data. So we remove that row.



## There are duplicate TCode entries in the s8 data frame. We need to get rid of them.
s8<-s8[-198, ]  
s8<-s8[-197, ]
s8<-s8[-196, ]
s8<-s8[-195, ]
s8<-s8[-194, ]
s8<-s8[-193, ]
s8<-s8[-192, ]
s8<-s8[-191, ]
s8<-s8[-190, ]
s8<-s8[-189, ]
s8<-s8[-188, ]

# Now lets try to merge the two files. But merging does not work because the two sets of variables in the two files do not match. PH has variables "Q3_10" and "BarrierHousing" that S8 does not. S8 has variables "Q30_Other" and "SSLanguage" that PH does not have. 

#summary(ph$Q3_10) # All 85 obs have the value NA.
#summary(s8$Q3_10) # NULL

#summary(ph$BarrierHousing) # All 85 observations have NA values.
#summary(s8$BarrierHousing) # NULL

#summary(s8$Q30_Other) # 255 obs have the value NA. The others have a value of 0.
#summary(ph$Q30_Other) # NULL

#summary(s8$SSLanguage) # This has useful data. It would be costly to delete this variable
#summary(ph$SSLanguage) # NULL




# Lets create variables Q3_10 and BarrierHousing for s8 and variables Q30_Other and SSLanguage for ph and assigned a value of NA to these variables. That made the two files have the same set of variables.

s8$Q3_10 <- NA
ph$Q30_Other <- NA
s8$BarrierHousing <- NA
ph$SSLanguage <- NA

# Now lets add the location codes to "ph" file from "ph_loc" file.
ph <- merge(phadditional, ph, by = "TCode", all=TRUE)
ph$location <- as.factor(ph$location)


s8 <- merge(s8additional, s8, by = "TCode", all=TRUE)
s8$location <- NA

# Next we create a new variable PH_or_S8 for both the files. This will be helpful in identifying which household is S8 and which is PH after we have merged the two files. 
ph$PH_or_S8 <- "PH"
s8$PH_or_S8 <- "S8"


# I notice that the file "s8" has Q11, Q17, Q19, Q20 coded differently than file "ph". So lets fix those.
#summary(s8$Q11)
s8$Q11 <- as.factor(as.integer(s8$Q11))
s8$Q11 <- factor(s8$Q11,
                 levels = c(1, 2, 3, 4, 5, 999),
                 labels = c("No, never", "Rarely", "Sometimes", "Most of the time", "Yes, all of the time", NA))
#summary(s8$Q17)
s8$Q17 <- as.factor(as.integer(s8$Q17))
s8$Q17 <- factor(s8$Q17,
                 levels = c(1, 2, 3, 4, 5, 999),
                 labels = c("No, never", "Yes, 1 time", "Yes, 2 times", "Yes, 3 times", "Yes, 4 times or more", NA))
#summary(s8$Q19)
s8$Q19 <- as.factor(as.integer(s8$Q19))
s8$Q19 <- factor(s8$Q19,
                 levels = c(1, 2, 999),
                 labels = c("Yes", "No", NA))
#summary(s8$Q20)
s8$Q20 <- as.factor(as.integer(s8$Q20))
s8$Q20 <- factor(s8$Q20,
                 levels = c(1, 2, 3, 4, 999),
                 labels = c("Yes, I currently have sufficient child care", "No, I currently have no child care, but need it", "No, I currently have some child care, but need more", "N/A, I currently do not need child care", NA))


## In order to check if we have included all the observations from the Excel file in our analysis, lets try to see if there are observations in the Excel file that do not exist in the SPSS file for S8.
# s8TCodesFromExcel <- read.csv("s8-listOfTCodes-fromExcel.csv")
# summary(s8TCodesFromExcel)

# s8_merged <- merge(s8, s8TCodesFromExcel, by = intersect(names(s8), names(s8TCodesFromExcel)), all=TRUE)
# s8_merged$TCode <- as.factor(s8_merged$TCode)
# summary(s8_merged$TCode)

# Now lets create the merged file. PH survey sent = 131 (received 85); S8 surveys sent = 273 (received 257).

ph$Q11 <- ordered(ph$Q11,
                  levels = c("No, never", "Rarely", "Sometimes", "Most of the time", "Yes, all of the time"),
                  labels = c("No, never", "Rarely", "Sometimes", "Most of the time", "Yes, all of the time"))
s8$Q11 <- ordered(s8$Q11,
                  levels = c("No, never", "Rarely", "Sometimes", "Most of the time", "Yes, all of the time"),
                  labels = c("No, never", "Rarely", "Sometimes", "Most of the time", "Yes, all of the time"))

# Check to see if the variables in S8 and PH are the same

#setdiff(names(s8), intersect(names(ph), names(s8)))
#setdiff(names(ph), intersect(names(ph), names(s8)))

names(ph)[names(ph)=="Rec.d"]<-"Recd."
names(ph)[names(ph)=="Scanned"]<-"Scanned."
names(ph)[names(ph)=="Sent.to.CU"]<-"Sent.to.CU."
names(ph)[names(ph)=="Non.Students.Age.18."]<-"Non.Students.Ages.18."

all <- rbind(ph, s8)
all$PH_or_S8<-as.factor(all$PH_or_S8)

all$Mailing.Zip<-as.factor(all$Mailing.Zip)
all$Member.Age...as.of.date<-as.numeric(all$Member.Age...as.of.date)
names(all)[names(ph)=="Member.Age...as.of.date"]<-"Age"
all$Total.Annual.Income<-as.numeric(all$Total.Annual.Income)
all$Member.Ethnicity<-as.factor(all$Member.Ethnicity)
all$Bedrooms<-as.factor(all$Bedrooms)
all$Family.Members<-as.factor(all$Family.Members)
all$Eligible..Members<-as.factor(all$Eligible..Members)
all$Dependants<-as.factor(all$Dependants)
all$HH.Members.under.age.13<-as.factor(all$HH.Members.under.age.13)
all$Student.Houshold.Members<-as.factor(all$Student.Houshold.Members)
all$Non.Students.Ages.18.<-as.factor(all$Non.Students.Ages.18.)
for(i in 1:length(all$Surveyed)) if(is.na(all$Surveyed[i])) all$Surveyed[i]<-"No"
all$Surveyed<-as.factor(all$Surveyed)

for(i in 1:length(all$Move.Out)) if(all$Move.Out[i]=="99-12-30") all$Move.Out[i]<-NA
#for(i in 1:length(all$Move.In)) if(all$Move.In[i]=="99-12-30") all$Move.In[i]<-NA

all$Movedout<-NA
all$Move.Out<-as.character(all$Move.Out)
for(i in 1:length(all$Move.Out)) 
  if(is.na(all$Move.Out[i])) all$Movedout[i]<-"No" else all$Movedout[i]<-"Yes"
all$Movedout<-as.factor(all$Movedout)
summary(all$Movedout)



ph<-all[all$PH_or_S8=="PH", ]
s8<-all[all$PH_or_S8=="S8", ]

pander(xtabs(formula = ~ s8$Q1 + s8$Movedout, data=s8))

write.csv(ph, file = "/home/anirban/Documents/BoulderHousingPartnersData/DATA_csv/ph.csv")
write.csv(s8, file = "/home/anirban/Documents/BoulderHousingPartnersData/DATA_csv/s8.csv")
write.csv(all, file = "/home/anirban/Documents/BoulderHousingPartnersData/DATA_csv/all.csv")
```

(2) the households that moved out vs. those that did not, assuming that there are enough of the former.  How did move out and how many of those were S8 and how many in PH?
```{r}
y<-subset(s8, Mailing.Zip==80304 | Mailing.Zip==80501 | Mailing.Zip==80301 | Mailing.Zip==80503 | Mailing.Zip==80303 | Mailing.Zip==80026)
summary(y$Mailing.Zip)
xtabs(formula = ~ y$Mailing.Zip + y$Movedout, data=y)
pander(xtabs(formula = ~ y$Q36_1 + y$Movedout, data=y))


summary(all$Move.Out)

xtabs(formula = ~all$PH_or_S8 + all$Movedout, data=all)
xtabs(formula = ~all$Single.Parent.HH + all$Movedout, data=all)
x <- subset(all, Surveyed=="Yes")
xtabs(formula = ~x$PH_or_S8 + x$Movedout, data=x)
x <- subset(x, PH_or_S8=="PH")
xtabs(formula = ~x$Single.Parent.HH + x$Movedout, data=x)

ggplot(ph, aes(Movedout, Age)) + geom_point(size=3, shape=1, alpha=0.8) + coord_flip() + 
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  )   

ggplot(ph, aes(Movedout, TTP)) + geom_boxplot(alpha=0.8) + coord_flip() + 
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  )

xtabs(formula = ~ph$Single.Parent.HH + ph$Movedout, data=ph)
xtabs(formula = ~ph$Member.Sex + ph$Movedout, data=ph)
xtabs(formula = ~ph$Member.Citizen + ph$Movedout, data=ph)



x <- subset(ph, Surveyed=="Yes")
xtabs(formula = ~x$Q2 + x$Movedout, data=x)
xtabs(formula = ~x$Q36_1 + x$Movedout, data=x)

summary(s8$Total.Annual.Income)
x <- subset(s8, Movedout=="Yes")
summary(x$Total.Annual.Income)
ggplot(s8, aes(Movedout, Total.Annual.Income)) + geom_boxplot(alpha=0.8) + coord_flip() + 
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  )

ggplot(s8, aes(Mailing.Zip, Total.Annual.Income)) + geom_point(shape=1, size=3, alpha=0.7) + coord_flip() + 
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  )
x<-summary(subset(s8$Mailing.Zip, !is.na(s8$Mailing.Zip)))
x<-as.table(x)
x<-as.data.frame(t(x))
names(x)[2]<-"Zip"
summary(x)

ggplot(x, aes(reorder(Zip, Freq), Freq)) + geom_bar(stat="identity") + geom_text(aes(label=Freq, vjust=-0.5), stat="identity", position="identity") +
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 0.5, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  )

y<-subset(s8, Mailing.Zip==80304 | Mailing.Zip==80501 | Mailing.Zip==80301 | Mailing.Zip==80503 | Mailing.Zip==80303 | Mailing.Zip==80026)
ggplot(y, aes(y$Mailing.Zip, Total.Annual.Income)) + geom_boxplot(aes(stat="middle")) +
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 0.5, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  )
######################## S8 movers vs non movers ################################################3

xtabs(formula = ~all$Single.Parent.HH + all$Movedout, data=all)
x <- subset(all, Surveyed=="Yes")
xtabs(formula = ~x$PH_or_S8 + x$Movedout, data=x)
x <- subset(x, PH_or_S8=="PH")
xtabs(formula = ~x$Single.Parent.HH + x$Movedout, data=x)


ggplot(s8, aes(Movedout, Age)) + geom_boxplot() + coord_flip() + 
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  )   

ggplot(s8, aes(Movedout, Age)) + geom_point(size=3, shape=1, alpha=0.8) + coord_flip() + 
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  )   

ggplot(s8, aes(Movedout, TTP)) + geom_point(size=3, shape=1, alpha=0.8) + coord_flip() + 
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  )

xtabs(formula = ~s8$Single.Parent.HH + s8$Movedout, data=s8)
xtabs(formula = ~s8$Member.Sex + s8$Movedout, data=s8)
xtabs(formula = ~s8$Member.Citizen + s8$Movedout, data=s8)



x <- subset(s8, Surveyed=="Yes")
xtabs(formula = ~x$Q2 + x$Movedout, data=x)
xtabs(formula = ~x$Q36_1 + x$Movedout, data=x)
xtabs(formula = ~x$Q25_1 + x$Movedout, data=x)
xtabs(formula = ~x$Q5 + x$Movedout, data=x)

```



```{r}
ggplot(all, aes(PH_or_S8, Age)) + geom_boxplot() + coord_flip() + 
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  )   

p<-subset(all, PH_or_S8=="PH")
s<-subset(all, PH_or_S8=="S8" & !is.na(Age))
median(p$Age)
median(s$Age)

median(p$Total.Annual.Income)
median(s$Total.Annual.Income)

x<-subset(all, all$Total.Annual.Income!=0)
p<-subset(x, PH_or_S8=="PH")
s<-subset(x, PH_or_S8=="S8" & !is.na(Age))
median(p$Total.Annual.Income)
median(s$Total.Annual.Income)

x<-subset(all, all$Total.Annual.Income!=0)
ggplot(x, aes(PH_or_S8, Total.Annual.Income)) + geom_boxplot() + coord_flip() + 
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  )   


ggplot(ph, aes(Surveyed, Tenant.Rent)) + geom_boxplot() + coord_flip() + 
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  )   

xtabs(formula = ~ph$Surveyed + ph$Member.Sex, data=ph)
round(prop.table(xtabs(formula = ~ph$Surveyed + ph$Member.Sex, data=ph), 2)*100, 0)

xtabs(formula = ~all$Surveyed + all$Member.Sex, data=all)
round(prop.table(xtabs(formula = ~ph$Member.Citizen+ph$Surveyed, data=ph), 1)*100, 0)
(round(prop.table(xtabs(formula = ~ph$Member.Citizen+ph$Surveyed, data=ph), 1)*100, 0))
pander(ftable(round(prop.table(xtabs(formula = ~ph$Member.Citizen+ph$Surveyed, data=ph), 1)*100, 0)))
table(ph$Member.Citizen, ph$Surveyed)
```

Are those who are younger
-more optimistic about the future need for housing assistance? Q2
-more likely to pay rent late? Q4
-different in employment status? Q5
-more likely to run out of income in last 3 months? Q9
-more likely to have food sources other than income? Q12
-more likely to say Hard to get to appts./work last 2 weeks? Q17
-more likely to receive food stamps Q25_1?
-health insurance Q28?
-how would you rate your current health Q29?
-medical problem and not go to a doctor? Q31
-highest level of education you have completed? Q32 

Are those who are earning more 
-more optimistic about the future need for housing assistance? Q2
-less likely to pay rent late? Q4
-different in employment status? Q5
-more likely to run out of income in the last 3 months? Q9
-more likely to have food sources other than income? Q12
-more likely to say Hard to get to appts./work last 2 weeks? Q17
-less likely to say they have children less than 13 years of age? Q19
-more likely to receive food stamps Q25_1?
-health insurance Q28?
-how would you rate your current health Q29?
-medical problem and not go to a doctor? Q31
-highest level of education you have completed? Q32 

```{r}
#######################################################################
ggplot(all, aes(Q2, Age)) + geom_jitter(alpha=0.6, shape=1, size=5, position = position_jitter(width = 0, height = 0.5)) + coord_flip() + 
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  ) 

ggplot(all, aes(Q2, Age)) + geom_boxplot() + coord_flip() +
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  ) 

#######################################################################
ggplot(all, aes(Q4, Age)) + geom_boxplot() + coord_flip() +
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  )   

#######################################################################
ggplot(all, aes(Q5, Age)) + geom_boxplot() + coord_flip() +
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  )   

#######################################################################
ggplot(all, aes(Q9, Age)) + geom_boxplot() + coord_flip() +
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  )   

#######################################################################
ggplot(all, aes(Q12, Age)) + geom_jitter(alpha=0.6, shape=1, size=5, position = position_jitter(width = 0, height = 0.5)) + coord_flip() +
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  ) 

x<-subset(all, !is.na(Q12))
ggplot(x, aes(Age, fill=Q12)) + geom_bar(position='dodge', binwidth=2) +
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  )
#######################################################################
ggplot(all, aes(Q17, Age)) + geom_boxplot() + coord_flip() +
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  )   
#######################################################################
ggplot(all, aes(Q25_1, Age)) + geom_jitter(alpha=0.6, shape=1, size=5, position = position_jitter(width = 0, height = 0.5)) + coord_flip() +
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  )   

x<-subset(all, !is.na(Q25_1))
ggplot(x, aes(Age, fill=Q25_1)) + geom_bar(position='dodge', binwidth=2) +
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  )
#######################################################################
ggplot(all, aes(Q28, Age)) + geom_boxplot() + coord_flip() +
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  )   

#######################################################################
ggplot(all, aes(Q29, Age)) + geom_boxplot() + coord_flip() +
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  )  

#######################################################################
ggplot(all, aes(Q31, Age)) + geom_jitter(alpha=0.6, shape=1, size=5, position = position_jitter(width = 0, height = 0.5)) + coord_flip() +
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  )  

x<-subset(all, !is.na(Q31))
ggplot(x, aes(Age, fill=Q31)) + geom_bar(position='dodge', binwidth=2) +
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  )

#######################################################################
ggplot(all, aes(Q32, Age)) + geom_boxplot() + coord_flip() +
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  )  
```


```{r}
#######################################################################
ggplot(all, aes(Q2, Total.Annual.Income)) + geom_boxplot() + coord_flip() +
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  ) 
#######################################################################
ggplot(all, aes(Q4, Total.Annual.Income)) + geom_boxplot() + coord_flip() +
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  ) 
#######################################################################
ggplot(all, aes(Q5, Total.Annual.Income)) + geom_boxplot() + coord_flip() +
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  )  
#######################################################################
ggplot(all, aes(Q9, Total.Annual.Income)) + geom_boxplot() + coord_flip() +
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  )   
#######################################################################
ggplot(all, aes(Q12, Total.Annual.Income)) + geom_jitter(alpha=0.6, shape=1, size=5, position = position_jitter(width = 0, height = 0.5)) + coord_flip() +
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  ) 

x<-subset(all, !is.na(Q12))
ggplot(x, aes(Total.Annual.Income, fill=Q12)) + geom_bar(position='dodge', binwidth=2000) +
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  ) 

#######################################################################
ggplot(all, aes(Q17, Total.Annual.Income)) + geom_boxplot() + coord_flip() +
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  )   

#######################################################################
x<-subset(all, !is.na(Q19))
ggplot(x, aes(Total.Annual.Income, fill=Q19)) + geom_bar(position='dodge', binwidth=8000) +
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  ) 

#######################################################################
x<-subset(all, !is.na(Q25_1))
ggplot(x, aes(Total.Annual.Income, fill=Q25_1)) + geom_bar(position='dodge', binwidth=8000) +
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  ) 

#######################################################################
ggplot(all, aes(Q28, Total.Annual.Income)) + geom_boxplot() + coord_flip() +
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  )   

#######################################################################
ggplot(all, aes(Q29, Total.Annual.Income)) + geom_boxplot() + coord_flip() +
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  )   


#######################################################################
ggplot(all, aes(Q31, Total.Annual.Income)) + geom_boxplot() + coord_flip() +
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  )   

x<-subset(all, !is.na(Q31))
ggplot(x, aes(Total.Annual.Income, fill=Q31)) + geom_bar(position='dodge', binwidth=8000) +
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  ) 

#######################################################################
ggplot(all, aes(Q32, Total.Annual.Income)) + geom_boxplot() + coord_flip() +
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  )   

```

Are those who have been in their current housing for a long time more likely to say that they expect to remain in BHP housing for 5 or more years? Q2

```{r}
x<-subset(all, !is.na(Move.Out))
x$Move.In1<-as.Date(x$Move.In)
x$Move.Out<-as.Date(x$Move.Out, "%y%m%d")
```


Are there more people who did not respond to the survey in some of the 5 ph locations than others?
```{r}
pander(xtabs(formula = ~ph$Surveyed+ph$location, data=ph))
prop.table(xtabs(formula = ~ph$Surveyed+ph$location, data=ph, 1))
xtabs(formula = ~ph$Surveyed+ph$location, data=ph)
```


Immigration status Q36_11 and Member.Citizen?
Immigration status Q36_11 and Eligible..Members?  
Member.Ethnicity and Hispanic/Latino Q38?
```{r}
summary(all$Q36_11)
xtabs(formula = ~all$Q36_11 + all$Member.Citizen, data=all)
xtabs(formula = ~all$Q36_11 + all$Eligible..Members, data=all)
xtabs(formula = ~all$Q38 + all$Member.Ethnicity, data=all)
```



```{r}
manipulate(ggplot(ph, aes(Movedout, Age)) + geom_point(size=3, shape=x, alpha=0.7) + coord_flip() + 
  theme(
    plot.title = element_text(size=20, face="bold", vjust=3, color="#000033"), 
    axis.text.x = element_text(size=15, angle = 0, hjust = 1, color="#000033"), 
    axis.text.y = element_text(color="#000033", size=15), 
    axis.title.x = element_text(color="#000033", size=15), 
    axis.title.y = element_text(color="#000033", size=15, vjust=2),
    legend.title=element_blank(),
    legend.text = element_text(colour="#000033", size = 15)
  ), x=slider(1,9))   
```



